Global patterns of forest autotrophic carbon fluxes

### 2020-01-20 manuscript/manuscript draft.Rmd
Table 2

\newpage  
| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Gross Primary Production | NA | flux partitioning of eddy-covariance; $NPP$+$R_{auto}$ | 243 | 49 |
| $NPP$ | Net Primary Production | stem, foliage, coarse root, fine root, optionally others (e.g., branch, reproductive, understory) | $ANPP$ + $BNPP$ (majority); $GPP$-$R_{auto}$ | 92 | 42 |
| $ANPP$ | Aboveground Net Primary Production | stem, foliage, optionally others (e.g., branch, reproductive, understory) (**issues [52](https://github.com/forc-db/Global_Productivity/issues/52), [54](https://github.com/forc-db/Global_Productivity/issues/54)**) |$ANPP_{woody-stem}$ + $ANPP_{foliage}$ (+ others) | 256 | 80 |
| $ANPP_{woody-stem}$ | Net Primary Production of woody stems | woody stems down to DBH $\le$ 10cm (no branch turnover) | direct measurement of stem growth increment (**with recruitment?**) | 264 | 96 |
| $ANPP_{foliage}$ | Net Primary Production of foliage | foliage | direct measurement of litterfall | 98 | 49 |
| $BNPP_{root}$  | Belowground Net Primary Production | coarse and fine roots |  coarse roots estimated indirectly using allometries based on aboveground stem increment measures ; fine roots as below | 101 | 48 |
| $BNPP_{fine.root}$ | Net Primary Production of fine roots | fine roots | measurements combined one or more of the following: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 88 | 41 |
| $R_{root}$ | Root Respiration | **coarse** and fine roots | *measurement of root gas exchange, root exclusion from soil respiration chambers* | 64 | 26 |
| $R_{auto}$ | Autotrophic Respiration | foliage, stem, and root | chamber measurements of component gas exchange | 22 | 13 |

>>>>

\newpage  
| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Gross Primary Production | NA | flux partitioning of eddy-covariance; $NPP$+$R_{auto}$ | 243 | 49 |
| $NPP$ | Net Primary Production | stem, foliage, coarse root, fine root, optionally others (e.g., branch, reproductive, understory) | $ANPP$ + $BNPP$ (majority); $GPP$-$R_{auto}$ | 92 | 42 |
| $ANPP$ | Aboveground Net Primary Production | stem, foliage, optionally others (e.g., branch, reproductive, understory) (**issues [52](https://github.com/forc-db/Global_Productivity/issues/52), [54](https://github.com/forc-db/Global_Productivity/issues/54)**) |$ANPP_{woody-stem}$ + $ANPP_{foliage}$ (+ others) | 256 | 80 |
| $ANPP_{woody-stem}$ | Net Primary Production of woody stems | woody stems down to DBH $\le$ 10cm (no branch turnover) | stem growth measurements scaled to biomass using allometries (**with recruitment?**) | 264 | 96 |
| $ANPP_{foliage}$ | Net Primary Production of foliage | foliage | litterfall collection (separated into components) | 98 | 49 |
| $BNPP_{root}$  | Belowground Net Primary Production | coarse and fine roots |  coarse roots estimated indirectly using allometries based on aboveground stem increment measures ; fine roots as below | 101 | 48 |
| $BNPP_{fine.root}$ | Net Primary Production of fine roots | fine roots | measurements combined one or more of the following: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 88 | 41 |
| $R_{root}$ | Root Respiration | **coarse** and fine roots | *measurement of root gas exchange, root exclusion from soil respiration chambers* | 64 | 26 |
| $R_{auto}$ | Autotrophic Respiration | foliage, stem, and root | chamber measurements of component gas exchange | 22 | 13 |
